PHQ-4-R - Data Cleaning (Study 2)

### 2024-02-27 study2/analysis/1_cleaning.qmd
add table
add progress bar

df <- read.csv("../data/data_raw.csv")
```

@@

@@

# TODO: compute modified score
# Maybe use the score_PHQ4 function from the README to demo it here

>>>>

df <- read.csv("../data/data_raw.csv") |> 
   mutate(across(everything(), ~ifelse(.x == "", NA, .x))) 
```

@@

# Table
summarize(df, N = n(), .by=c("Experimenter")) |> 
  arrange(desc(N)) |> 
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) |> 
  gt::tab_header("Number of participants per recruitment source")
```

@@
